---
title: "MIS530Module8"
author: "Taylor Weese"
date: "2/9/2020"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data import and sample
```{r import}
library(ggplot2)
library(dplyr)
library(Hmisc)
library(cowplot)
library(WVPlots)
set.seed(123)
Data <- read.csv("influenza.csv")
sample_n(Data, 5)
```

## Understanding the data

* **Season**: Date range of when data was being collected by the CDC 
* **Region**: Region where data was collected
* **County**: County where data was collected
* **CDC.Week**: term for the CDC
* **Week.Ending.Date**: the conclusion of data being retrieved by the CDC
* **Disease**: identifies which influenza strand was diagnosed by the CDC *#predicted value*
* **Count**: how many of each influenza disease was diagnosed during a season, in a region and county
* **County.Centroid**: GPS location
* **FIPS**: Postal Code

```{r describe}
describe(Data)
```

No missing values at this point in the dataset. 

## Exploratory Data Analysis
```{r Exploratory}
## find the type of variable for each column
str(Data)
## show the first six rows for each column
head(Data)
## summary of statistics for each column
summary(Data)
##Correlations
x <- ggplot(Data, aes(Disease, Count)) +
  geom_jitter(color = "blue", alpha = 0.5) +
    theme_light()
y <- ggplot(Data, aes(Region, Count)) +
  geom_jitter(color = "green", alpha = 0.5) +
  theme_light()
p <- plot_grid(x, y) 
title <- ggdraw() + draw_label("Correlation between Count and Region / Disease", fontface='bold')
plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1))
```

## Linear Regression Model/Preparation and splitting the data
```{r Linear}
set.seed(2)
train.index <- sample(c(1:dim(Data)[1]), dim(Data)[1]*0.6)  
train.df <- Data[train.index, ]
valid.df <- Data[-train.index, ]
```
# use lm() to run a linear regression of Count on all predictors in the training set
```{r Count}
Data.lm <- lm(Count ~ ., data = train.df)
options(scipen = 999)
summary(Data.lm)
```
# Execute scatter plot for Disease and Count with y-intercept
```{r Disease}
plot(Data$Disease, Data$Count)
Data.lm2 <- lm(Data$Count ~ Data$Count)
Data.lm2
abline(Data.lm2, col="red")
```

# Execute scatter plot for Region and Count with y-intercept
```{r Region}
plot(Data$Region, Data$Count)
Data.lm2 <- lm(Data$Count ~ Data$Region)
Data.lm2
abline(Data.lm2, col="red")
```